Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex

    \end{tikzpicture}
    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
    the central vertex in the diamond is removed, then a subgraph isomorphism exists.}
    \label{figure:subgraphexample}
\end{figure}

@@

A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping $P
\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
isomorphism $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
We define a $k$-less subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all but
$k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
\lessind{k} T$ respectively.

The \emph{complement} of a (simple) graph $P$ is the graph $\shortoverline{P}~$.  Adjacent distinct
vertices in $P$ are non-adjacent in $\shortoverline{P}$ while non-adjacent vertices in $P$ are
adjacent in $\shortoverline{P}$.  The \emph{loop complement} of a graph $P$ is the graph
$\loopcomp{P}$.  The construction of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however
whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an
induced subgraph isomorphism problem we make use of the loop complement; we care about mapping
vertices with loops to vertices with loops, and vertices without loops to vertices without loops.
The following proposition follows directly from the definitions.

>>>>

    \end{tikzpicture}
    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
    the central vertex in $P$ is removed, then a subgraph isomorphism exists.}
    \label{fig:subgraphexample}
\end{figure}

@@

A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping $P
\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
isomorphism} $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
We define a \emph{$k$-less subgraph isomorphism} from $P$ to $T$ to be a subgraph isomorphism from all but
$k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
\lessind{k} T$ respectively.

The \emph{complement} of a (simple) graph $P$ is the graph $\shortoverline{P}~$.  Adjacent distinct
vertices in $P$ are non-adjacent in $\shortoverline{P}$ while non-adjacent vertices in $P$ are
adjacent in $\shortoverline{P}$.  The \emph{loop complement} of a graph $P$ is the graph
$\loopcomp{P}$.  The construction of $\loopcomp{P}$ is similar to that of $\shortoverline{P}~$, however
whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an
induced subgraph isomorphism problem we make use of the loop complement; we care about mapping
vertices with loops to vertices with loops, and vertices without loops to vertices without loops.
The following proposition follows directly from the definitions.
